---
title: "Create Sahel Maps"
authors: "Bernhard Bieri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create Sahel Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setting things up:

This vignette describes a workflow on how to easily create maps for the project
with `{SahelGraphR}`. Before starting, we need to load a few packages which
will be required to download the data.

```{r setup}
library(SahelGraphR)
library(tidyverse)
library(patchwork)
```

Once this is done, we proceed and use the `get_shapefiles()` function from
our package to download the shapefiles for the desired countries at the desired
level. Note that Mauritania's shapefiles are only availiable until level 2 and not
3.

```{r download}
(SEN <- get_shapefiles(country_code = "SEN", level = 2) |>
    dplyr::rename(ADM2_NAME = ADM2_FR) |>
    dplyr::select(ADM2_NAME, geometry))
(BFA <- get_shapefiles(country_code = "BFA", level = 2) |>
    dplyr::rename(ADM2_NAME = adm2_name1) |>
    dplyr::select(ADM2_NAME, geometry))
(NER <- get_shapefiles(country_code = "NER", level = 2) |>
    dplyr::rename(ADM2_NAME = adm_02) |>
    dplyr::select(ADM2_NAME, geometry))
(MRT <- get_shapefiles(country_code = "MRT", level = 2) |>
    dplyr::rename(ADM2_NAME = ADM2_EN) |>
    dplyr::select(ADM2_NAME, geometry))
```

Now that the downloads have successfully been completed, we can start plotting
the maps. We start with a series of individual plots and a `{patchwork}` plot.

```{r patchwork}
SEN_MAP <- ggplot2::ggplot(SEN) +
  ggplot2::geom_sf(ggplot2::aes(fill = ADM2_NAME)) +
  ggplot2::scale_fill_manual(values = asp_palette("Countries", 45, type = "continuous"),
                             guide = "none")  +
  ggplot2::labs(title = "Senegal") +
  themeaspdark()

SEN_MAP

BFA_MAP <- ggplot2::ggplot(BFA) +
  ggplot2::geom_sf(ggplot2::aes(fill = ADM2_NAME)) +
  ggplot2::scale_fill_manual(values = asp_palette("Countries", 45, type = "continuous"),
                             guide = "none")  +
  ggplot2::labs(title = "Burkina Faso") +
  themeaspdark()

BFA_MAP

NER_MAP <- ggplot2::ggplot(NER) +
  ggplot2::geom_sf(ggplot2::aes(fill = ADM2_NAME)) +
  ggplot2::scale_fill_manual(values = asp_palette("Countries", 67, type = "continuous"),
                             guide = "none")  +
  ggplot2::labs(title = "Niger") +
  themeaspdark()

MRT_MAP <- ggplot2::ggplot(MRT) +
  ggplot2::geom_sf(ggplot2::aes(fill = ADM2_NAME)) +
  ggplot2::scale_fill_manual(values = asp_palette("Countries", 57, type = "continuous"),
                             guide = "none")  +
  ggplot2::labs(title = "Mauritania") +
  themeaspdark()

MRT_MAP

# Patchwork
SEN_MAP + BFA_MAP + NER_MAP + MRT_MAP
```

Finally, we move to merge all of the shapefiles we previously consistently named
and plot the regional map. Make sure to use the same projections here!

```{r}
SAHEL_MAP <- ggplot2::ggplot(rbind(SEN, BFA, MRT, NER)) +
  ggplot2::geom_sf(ggplot2::aes(fill = ADM2_NAME)) +
  ggplot2::scale_fill_manual(values = asp_palette("Countries", 214, type = "continuous"),
                             guide = "none")  +
  ggplot2::labs(title = "Sahel ASP Countries") +
  themeaspdark()
SAHEL_MAP
```
